Preprocessing_&_Plot_for_Moral_Categ_Replication

### 2018-06-26 Replication/Results/data_analysis/preproc/Analysis_exp7_prepro.rmd
raincloud plot

```{r plot_match_RT_data,echo=FALSE,warning=FALSE, message=FALSE}
RTdata1 <- df.L1.V.sum_rt_acc_l %>%
  select(Subject,Match,Morality,Identity,RT) %>% 
  filter(Match == "match" & Morality == "Good")
RTdata1$Identity <- factor(RTdata1$Identity,levels = c("Self","Other"))
p1 <- ggbetweenstats(data = RTdata1, x = Identity, y = RT,  
                     xlab = "Good", ylab = "Reaction times (ms)",
                     type = FALSE) + theme_classic() + theme(legend.position = "none",
                                                             text=element_text(family='Times'),
                                                             axis.line.x=element_line(size=1.2),
                                                             axis.line.y=element_line(size=1.2),
                                                             axis.title.x =element_text(size=16), 
                                                             axis.title.y=element_text(size=16),
                                                             axis.text.x=element_text(size=14, color = "black"),
                                                             axis.text.y=element_text(size=14, color = "black"),
                                                             axis.ticks.x=element_line(size=1.2),
                                                             axis.ticks.y=element_line(size=1.2))

RTdata2 <- df.L1.V.sum_rt_acc_l %>%
  select(Subject,Match,Morality,Identity,RT) %>% 
  filter(Match == "match" & Morality == "Bad")
RTdata2$Identity <- factor(RTdata2$Identity,levels = c("Self","Other"))
p2 <- ggbetweenstats(data = RTdata2, x = Identity, y = RT,  
                     xlab = "Bad", ylab = "",
                     type = FALSE) + theme_classic() + theme(legend.position = "none",
                                                             text=element_text(family='Times'),
                                                             axis.line.x=element_line(size=1.2),
                                                             axis.title.x =element_text(size=16),
                                                             axis.text.x=element_text(size=14,color = "black"),
                                                             axis.ticks.x=element_line(size=1.2)) +scale_y_continuous(breaks = NULL)
setwd(traDir)
tiff("p_rt_match.tiff", width = 9, height = 6, units = 'in', res = 300)
p_rt_match <- multiplot(p1,p2,cols = 2)
dev.off()
setwd(curDir)
multiplot(p1,p2,cols = 2)
```

```{r plot_match_dprime_data,echo=FALSE,warning=FALSE, message=FALSE}
Ddata1 <- df.L1.V.SDT_l %>%
  select(Subject,Morality,Identity,dprime) %>% 
  filter(Morality == "Good")
Ddata1$Identity <- factor(Ddata1$Identity,levels = c("Self","Other"))
p1 <- ggbetweenstats(data = Ddata1, x = Identity, y = dprime,  
                     xlab = "Good", ylab = "d prime",
                     type = FALSE) + theme_classic() + theme(legend.position = "none",
                                                             text=element_text(family='Times'),
                                                             axis.line.x=element_line(size=1.2),
                                                             axis.line.y=element_line(size=1.2),
                                                             axis.title.x =element_text(size=16), 
                                                             axis.title.y=element_text(size=16),
                                                             axis.text.x=element_text(size=14, color = "black"),
                                                             axis.text.y=element_text(size=14, color = "black"),
                                                             axis.ticks.x=element_line(size=1.2),
                                                             axis.ticks.y=element_line(size=1.2))

Ddata2 <- df.L1.V.SDT_l %>%
  select(Subject,Morality,Identity,dprime) %>% 
  filter(Morality == "Bad")
Ddata2$Identity <- factor(RTdata2$Identity,levels = c("Self","Other"))
p2 <- ggbetweenstats(data = Ddata2, x = Identity, y = dprime,  
                     xlab = "Bad", ylab = "",
                     type = FALSE) + theme_classic() + theme(legend.position = "none",
                                                             text=element_text(family='Times'),
                                                             axis.line.x=element_line(size=1.2),
                                                             axis.title.x =element_text(size=16),
                                                             axis.text.x=element_text(size=14,color = "black"),
                                                             axis.ticks.x=element_line(size=1.2)) +scale_y_continuous(breaks = NULL)
p_dprime_match <- multiplot(p1,p2,cols = 2)
# ggsave("p_rt_match.pdf", p_rt_match, scale = 1,height = 6, width = 8, dpi = 300, family = "Times")
setwd(traDir)
tiff("p_dprime_match.tiff", width = 9, height = 6, units = 'in', res = 300)
p_dprime_match <- multiplot(p1,p2,cols = 2)
dev.off()
setwd(curDir)
#multiplot(p1,p2,cols = 2)
```

```{r plot_categ_ACC_val_data,echo=FALSE,warning=FALSE, message=FALSE}
ACCdata1 <- df.T1.V.sum_rt_acc_l %>%
  select(Subject,Task,Morality,Identity,ACC) %>% 
  filter(Task == "Val"& Morality == 'Good')
ACCdata1$Identity <- factor(ACCdata1$Identity,levels = c("Self","Other"))
p1 <- ggbetweenstats(data = ACCdata1, x = Identity, y = ACC,  
                     xlab = "Good", ylab = "Accuracy",
                     type = FALSE) + theme_classic() + theme(legend.position = "none",
                                                             text=element_text(family='Times'),
                                                             axis.line.x=element_line(size=1.2),
                                                             axis.line.y=element_line(size=1.2),
                                                             axis.title.x =element_text(size=16), 
                                                             axis.title.y=element_text(size=16),
                                                             axis.text.x=element_text(size=14, color = "black"),
                                                             axis.text.y=element_text(size=14, color = "black"),
                                                             axis.ticks.x=element_line(size=1.2),
                                                             axis.ticks.y=element_line(size=1.2))

ACCdata2 <- df.T1.V.sum_rt_acc_l %>%
  select(Subject,Task,Morality,Identity,ACC) %>% 
  filter(Task == "Val"& Morality == 'Bad')
ACCdata2$Identity <- factor(ACCdata2$Identity,levels = c("Self","Other"))
p2 <- ggbetweenstats(data = ACCdata2, x = Identity, y = ACC,  
                     xlab = "Bad", ylab = "",
                     type = FALSE) + theme_classic() + theme(legend.position = "none",
                                                             text=element_text(family='Times'),
                                                             axis.line.x=element_line(size=1.2),
                                                             axis.title.x =element_text(size=16),
                                                             axis.text.x=element_text(size=14,color = "black"),
                                                             axis.ticks.x=element_line(size=1.2)) +scale_y_continuous(breaks = NULL)
setwd(traDir)
tiff("p_rt_match.tiff", width = 9, height = 6, units = 'in', res = 300)
p_rt_match <- multiplot(p1,p2,cols = 2)
dev.off()
setwd(curDir)
multiplot(p1,p2,cols = 2)
```

```{r plot_categ_ACC_ID_data,echo=FALSE,warning=FALSE, message=FALSE}
ACCdata1 <- df.T1.V.sum_rt_acc_l %>%
  select(Subject,Task,Morality,Identity,ACC) %>% 
  filter(Task == "Id"& Morality == 'Good')
ACCdata1$Identity <- factor(ACCdata1$Identity,levels = c("Self","Other"))
p1 <- ggbetweenstats(data = ACCdata1, x = Identity, y = ACC,  
                     xlab = "Good", ylab = "Accuracy",
                     type = FALSE) + theme_classic() + theme(legend.position = "none",
                                                             text=element_text(family='Times'),
                                                             axis.line.x=element_line(size=1.2),
                                                             axis.line.y=element_line(size=1.2),
                                                             axis.title.x =element_text(size=16), 
                                                             axis.title.y=element_text(size=16),
                                                             axis.text.x=element_text(size=14, color = "black"),
                                                             axis.text.y=element_text(size=14, color = "black"),
                                                             axis.ticks.x=element_line(size=1.2),
                                                             axis.ticks.y=element_line(size=1.2))

ACCdata2 <- df.T1.V.sum_rt_acc_l %>%
  select(Subject,Task,Morality,Identity,ACC) %>% 
  filter(Task == "Id"& Morality == 'Bad')
ACCdata2$Identity <- factor(ACCdata2$Identity,levels = c("Self","Other"))
p2 <- ggbetweenstats(data = ACCdata2, x = Identity, y = ACC,  
                     xlab = "Bad", ylab = "",
                     type = FALSE) + theme_classic() + theme(legend.position = "none",
                                                             text=element_text(family='Times'),
                                                             axis.line.x=element_line(size=1.2),
                                                             axis.title.x =element_text(size=16),
                                                             axis.text.x=element_text(size=14,color = "black"),
                                                             axis.ticks.x=element_line(size=1.2)) +scale_y_continuous(breaks = NULL)
setwd(traDir)
tiff("p_rt_match.tiff", width = 9, height = 6, units = 'in', res = 300)
p_rt_match <- multiplot(p1,p2,cols = 2)
dev.off()
setwd(curDir)
multiplot(p1,p2,cols = 2)
```

```{r plot_categ_RT_val_data,echo=FALSE,warning=FALSE, message=FALSE}
RTdata1 <- df.T1.V.sum_rt_acc_l %>%
  select(Subject,Task,Morality,Identity,RT) %>% 
  filter(Task == "Val"& Morality == 'Good')
RTdata1$Identity <- factor(RTdata1$Identity,levels = c("Self","Other"))
p1 <- ggbetweenstats(data = RTdata1, x = Identity, y = RT,  
                     xlab = "Good", ylab = "Reaction times (ms)",
                     type = FALSE) + theme_classic() + theme(legend.position = "none",
                                                             text=element_text(family='Times'),
                                                             axis.line.x=element_line(size=1.2),
                                                             axis.line.y=element_line(size=1.2),
                                                             axis.title.x =element_text(size=16), 
                                                             axis.title.y=element_text(size=16),
                                                             axis.text.x=element_text(size=14, color = "black"),
                                                             axis.text.y=element_text(size=14, color = "black"),
                                                             axis.ticks.x=element_line(size=1.2),
                                                             axis.ticks.y=element_line(size=1.2))

RTdata2 <- df.T1.V.sum_rt_acc_l %>%
  select(Subject,Task,Morality,Identity,RT) %>% 
  filter(Task == "Val"& Morality == 'Bad')
RTdata2$Identity <- factor(RTdata2$Identity,levels = c("Self","Other"))
p2 <- ggbetweenstats(data = RTdata2, x = Identity, y = RT,  
                     xlab = "Bad", ylab = "",
                     type = FALSE) + theme_classic() + theme(legend.position = "none",
                                                             text=element_text(family='Times'),
                                                             axis.line.x=element_line(size=1.2),
                                                             axis.title.x =element_text(size=16),
                                                             axis.text.x=element_text(size=14,color = "black"),
                                                             axis.ticks.x=element_line(size=1.2)) +scale_y_continuous(breaks = NULL)
setwd(traDir)
tiff("p_rt_match.tiff", width = 9, height = 6, units = 'in', res = 300)
p_rt_match <- multiplot(p1,p2,cols = 2)
dev.off()
setwd(curDir)
multiplot(p1,p2,cols = 2)
```

```{r plot_categ_RT_Id_data,echo=FALSE,warning=FALSE, message=FALSE}
RTdata1 <- df.T1.V.sum_rt_acc_l %>%
  select(Subject,Task,Morality,Identity,RT) %>% 
  filter(Task == "Id"& Morality == 'Good')
RTdata1$Identity <- factor(RTdata1$Identity,levels = c("Self","Other"))
p1 <- ggbetweenstats(data = RTdata1, x = Identity, y = RT,  
                     xlab = "Good", ylab = "Reaction times (ms)",
                     type = FALSE) + scale_y_continuous(limits = c(300,900),breaks = seq(300,900,100)) +
                     theme_classic() + theme(legend.position = "none",
                                                             text=element_text(family='Times'),
                                                             axis.line.x=element_line(size=1.2),
                                                             axis.line.y=element_line(size=1.2),
                                                             axis.title.x =element_text(size=16), 
                                                             axis.title.y=element_text(size=16),
                                                             axis.text.x=element_text(size=14, color = "black"),
                                                             axis.text.y=element_text(size=14, color = "black"),
                                                             axis.ticks.x=element_line(size=1.2),
                                                             axis.ticks.y=element_line(size=1.2)) +scale_y_continuous(breaks = NULL)
                    #+ coord_cartesian(ylim=c(300,900))

#y_scale <- scale_y_continuous(limits = range(RTdata1$RT))
RTdata2 <- df.T1.V.sum_rt_acc_l %>%
  select(Subject,Task,Morality,Identity,RT) %>% 
  filter(Task == "Id"& Morality == 'Bad')
RTdata2$Identity <- factor(RTdata2$Identity,levels = c("Self","Other"))
p2 <- ggbetweenstats(data = RTdata2, x = Identity, y = RT,  
                     xlab = "Bad", ylab = "",
                     type = FALSE)+
      scale_y_continuous(limits = c(300,900),breaks = seq(300,900,100)) +
      theme_classic() +
      theme(legend.position = "none",text=element_text(family='Times'),
                               axis.line.x=element_line(size=1.2),
                               axis.title.x =element_text(size=16),
                               axis.text.x=element_text(size=14,color = "black"),
                               axis.ticks.x=element_line(size=1.2))

@@

>>>>

```{r plot_match_RT_data,echo=FALSE,warning=FALSE, message=FALSE}
RTdata1 <- df.L1.V.sum_rt_acc_l %>%
  select(Subject,Match,Morality,Identity,RT) %>% 
  filter(Match == "match" & Morality == "Good")
RTdata1$Identity <- factor(RTdata1$Identity,levels = c("Self","Other"))
p1 <- ggplot(data = RTdata1, aes(y = RT, x = Identity,fill = Identity)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0)) +
  geom_point(aes(y = RT,color = Identity), position = position_jitter(width = .15), size = .5) +
  geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
  guides(fill = FALSE) +guides(color = FALSE)+
  theme_bw() +
  raincloud_theme+scale_y_continuous(limits = c(300,900))+labs(x = "Good",y = "Reaction times(ms)")
RTdata2 <- df.L1.V.sum_rt_acc_l %>%
  select(Subject,Match,Morality,Identity,RT) %>% 
  filter(Match == "match" & Morality == "Bad")
RTdata2$Identity <- factor(RTdata2$Identity,levels = c("Self","Other"))
p2 <- ggplot(data = RTdata2, aes(y = RT, x = Identity,fill = Identity)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0)) +
  geom_point(aes(y = RT,color = Identity), position = position_jitter(width = .15), size = .5) +
  geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
  guides(fill = FALSE) +guides(color = FALSE)+
  theme_bw() +
  raincloud_theme+scale_y_continuous(limits = c(300,900),breaks = NULL)+labs(x = "Bad",y = "")

@@

```{r plot_match_dprime_data,echo=FALSE,warning=FALSE, message=FALSE}
Ddata1 <- df.L1.V.SDT_l %>%
  select(Subject,Morality,Identity,dprime) %>% 
  filter(Morality == "Good")
Ddata1$Identity <- factor(Ddata1$Identity,levels = c("Self","Other"))
p1 <- ggplot(data = Ddata1, aes(y = dprime, x = Identity,fill = Identity)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0)) +
  geom_point(aes(y = dprime,color = Identity), position = position_jitter(width = .15), size = .5) +
  geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
  guides(fill = FALSE) +guides(color = FALSE)+
  theme_bw() +
  raincloud_theme+scale_y_continuous(limits = c(0,4))+labs(x = "Good",y = "dprime")
Ddata2 <- df.L1.V.SDT_l %>%
  select(Subject,Morality,Identity,dprime) %>% 
  filter(Morality == "Bad")
Ddata2$Identity <- factor(RTdata2$Identity,levels = c("Self","Other"))
p2 <- ggplot(data = Ddata2, aes(y = dprime, x = Identity,fill = Identity)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0)) +
  geom_point(aes(y = dprime,color = Identity), position = position_jitter(width = .15), size = .5) +
  geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
  guides(fill = FALSE) +guides(color = FALSE)+
  theme_bw() +
  raincloud_theme+scale_y_continuous(limits = c(0,4),breaks = NULL)+labs(x = "Bad",y = "")
p_dprime_match <- multiplot(p1,p2,cols = 2)
# ggsave("p_rt_match.pdf", p_rt_match, scale = 1,height = 6, width = 8, dpi = 300, family = "Times")
setwd(traDir)
tiff("p_dprime_match.tiff", width = 9, height = 6, units = 'in', res = 300)
p_dprime_match <- multiplot(p1,p2,cols = 2)
dev.off()
setwd(curDir)
#multiplot(p1,p2,cols = 2)
```

```{r plot_categ_ACC_val_data,echo=FALSE,warning=FALSE, message=FALSE}
ACCdata1 <- df.T1.V.sum_rt_acc_l %>%
  select(Subject,Task,Morality,Identity,ACC) %>% 
  filter(Task == "Val"& Morality == 'Good')
ACCdata1$Identity <- factor(ACCdata1$Identity,levels = c("Self","Other"))
p1 <- ggplot(data = ACCdata1, aes(y = ACC, x = Identity,fill = Identity)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0)) +
  geom_point(aes(y = ACC,color = Identity), position = position_jitter(width = .15), size = .5) +
  geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
  guides(fill = FALSE) +guides(color = FALSE)+
  theme_bw() +
  raincloud_theme+scale_y_continuous(limits = c(0,1))+labs(x = "Good",y = "Accuracy")

ACCdata2 <- df.T1.V.sum_rt_acc_l %>%
  select(Subject,Task,Morality,Identity,ACC) %>% 
  filter(Task == "Val"& Morality == 'Bad')
ACCdata2$Identity <- factor(ACCdata2$Identity,levels = c("Self","Other"))
p2 <- ggplot(data = ACCdata2, aes(y = ACC, x = Identity,fill = Identity)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0)) +
  geom_point(aes(y = ACC,color = Identity), position = position_jitter(width = .15), size = .5) +
  geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
  guides(fill = FALSE) +guides(color = FALSE)+
  theme_bw() +
  raincloud_theme+scale_y_continuous(limits = c(0,1),breaks = NULL)+labs(x = "Bad",y = "")
setwd(traDir)
tiff("p_rt_match.tiff", width = 9, height = 6, units = 'in', res = 300)
p_rt_match <- multiplot(p1,p2,cols = 2)
dev.off()
setwd(curDir)
multiplot(p1,p2,cols = 2)
```

```{r plot_categ_ACC_ID_data,echo=FALSE,warning=FALSE, message=FALSE}
ACCdata1 <- df.T1.V.sum_rt_acc_l %>%
  select(Subject,Task,Morality,Identity,ACC) %>% 
  filter(Task == "Id"& Morality == 'Good')
ACCdata1$Identity <- factor(ACCdata1$Identity,levels = c("Self","Other"))
p1 <- ggplot(data = ACCdata1, aes(y = ACC, x = Identity,fill = Identity)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0)) +
  geom_point(aes(y = ACC,color = Identity), position = position_jitter(width = .15), size = .5) +
  geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
  guides(fill = FALSE) +guides(color = FALSE)+
  theme_bw() +
  raincloud_theme+scale_y_continuous(limits = c(0,1))+labs(x = "Good",y = "Accuracy")
ACCdata2 <- df.T1.V.sum_rt_acc_l %>%
  select(Subject,Task,Morality,Identity,ACC) %>% 
  filter(Task == "Id"& Morality == 'Bad')
ACCdata2$Identity <- factor(ACCdata2$Identity,levels = c("Self","Other"))
p2 <- ggplot(data = ACCdata2, aes(y = ACC, x = Identity,fill = Identity)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0)) +
  geom_point(aes(y = ACC,color = Identity), position = position_jitter(width = .15), size = .5) +
  geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
  guides(fill = FALSE) +guides(color = FALSE)+
  theme_bw() +
  raincloud_theme+scale_y_continuous(limits = c(0,1),breaks = NULL)+labs(x = "Bad",y = "")
setwd(traDir)
tiff("p_rt_match.tiff", width = 9, height = 6, units = 'in', res = 300)
p_rt_match <- multiplot(p1,p2,cols = 2)
dev.off()
setwd(curDir)
multiplot(p1,p2,cols = 2)
```

```{r plot_categ_RT_val_data,echo=FALSE,warning=FALSE, message=FALSE}
RTdata1 <- df.T1.V.sum_rt_acc_l %>%
  select(Subject,Task,Morality,Identity,RT) %>% 
  filter(Task == "Val"& Morality == 'Good')
RTdata1$Identity <- factor(RTdata1$Identity,levels = c("Self","Other"))
p1 <- ggplot(data = RTdata1, aes(y = RT, x = Identity,fill = Identity)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0)) +
  geom_point(aes(y = RT,color = Identity), position = position_jitter(width = .15), size = .5) +
  geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
  guides(fill = FALSE) +guides(color = FALSE)+
  theme_bw() +
  raincloud_theme+scale_y_continuous(limits = c(300,900))+labs(x = "Good",y = "Reaction times(ms)")
RTdata2 <- df.T1.V.sum_rt_acc_l %>%
  select(Subject,Task,Morality,Identity,RT) %>% 
  filter(Task == "Val"& Morality == 'Bad')
RTdata2$Identity <- factor(RTdata2$Identity,levels = c("Self","Other"))
p2 <- ggplot(data = RTdata2, aes(y = RT, x = Identity,fill = Identity)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0)) +
  geom_point(aes(y = RT,color = Identity), position = position_jitter(width = .15), size = .5) +
  geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
  guides(fill = FALSE) +guides(color = FALSE)+
  theme_bw() +
  raincloud_theme+scale_y_continuous(limits = c(300,900),breaks = NULL)+labs(x = "Bad",y = "")

```{r plot_categ_RT_Id_data,echo=FALSE,warning=FALSE, message=FALSE}
RTdata1 <- df.T1.V.sum_rt_acc_l %>%
  select(Subject,Task,Morality,Identity,RT) %>% 
  filter(Task == "Id"& Morality == 'Good')
RTdata1$Identity <- factor(RTdata1$Identity,levels = c("Self","Other"))
p1 <- ggplot(data = RTdata1, aes(y = RT, x = Identity,fill = Identity)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0)) +
  geom_point(aes(y = RT,color = Identity), position = position_jitter(width = .15), size = .5) +
  geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
  guides(fill = FALSE) +guides(color = FALSE)+
  theme_bw() +
  raincloud_theme+scale_y_continuous(limits = c(300,900))+labs(x = "Good",y = "Reaction times(ms)")
                    #+ coord_cartesian(ylim=c(300,900))

#y_scale <- scale_y_continuous(limits = range(RTdata1$RT))
RTdata2 <- df.T1.V.sum_rt_acc_l %>%
  select(Subject,Task,Morality,Identity,RT) %>% 
  filter(Task == "Id"& Morality == 'Bad')
RTdata2$Identity <- factor(RTdata2$Identity,levels = c("Self","Other"))
p2 <- ggplot(data = RTdata2, aes(y = RT, x = Identity,fill = Identity)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0)) +
  geom_point(aes(y = RT,color = Identity), position = position_jitter(width = .15), size = .5) +
  geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
  guides(fill = FALSE) +guides(color = FALSE)+
  theme_bw() +
  raincloud_theme+scale_y_continuous(limits = c(300,900),breaks = NULL)+labs(x = "Bad",y = "")
